% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode,14pt]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Aditya Yedetore}
\newcommand{\CVTitle}{Aditya Yedetore's CV}
\newcommand{\CVNote}{CV compiled on {\today} } %for UIUC Summer Reasearch}
\newcommand{\CVWebpage}{http://www.adityayedetore.com}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{https://www.google.com/maps/place/2505+Meadow+Square+Ln,+Champaign,+IL+61822}
{2505 Meadow Square Ln. Champaign, IL, 61822} \\
\href{mailto:ayedeto1@jhu.edu}
{ayedeto1@jhu.edu}
\,\SubBulletSymbol\,
+1\,(617)\,678-2711
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{https://www.jhu.edu}
{\textbf{Johns Hopkins University}},
Baltimore, MD, USA

\Gap
\BulletItem
Double Majoring in 
\href{https://www.cs.jhu.edu}
{\textbf{Computer Science}}
and 
\href{https://cogsci.jhu.edu}
{\textbf{Cognitive Science}}
\hfill
\DatestampYM{2018}{8} -- 
\DatestampYM{2021}{12}

\begin{Detail}
	\SubBulletItem
	Cumulative GPA: 3.75 / 4.0
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}

\Entry
\href{https://www.halberdalab.net/}
    {\textbf{Vision and Cognition Lab}},
Undergraduate Research
\hfill
\DatestampYMD{2019}{08}{19} --
Present

%\BulletItem Built website to run experiment that probed human representation of collective/distributive events in the visual system and their interaction with quantifiers (``all'', ``each'') in the linguistic system.
\BulletItem Built a website to run an experiment that probed the interaction between the human object processing system and the linguistic system. 
\BulletItem Crowdsourced experiment participants with MTurk.
\BulletItem Processed and analyzed data collected, and performed statistical tests that produced results supporting our hypothesis about collective/distributive events. 

\Gap
\Gap
\Entry
\href{http://www.example.com/my-institute}
{\textbf{Computational Psycholinguistics Lab}},
Undergraduate Research
\hfill
\DatestampYMD{2020}{01}{20} --
Present

%TODO: change this, yamaini says flip first and second bullets, and make each bullet stand alone
\BulletItem Implemented an experiment to determine if neural networks could learn the syntactic rules of English Question formation from the data available to children. 
\BulletItem Collected and processed data from CHILDES (an online database made up of the speech children might hear when learning a language). 
\BulletItem Trained recurrent neural networks on that data, and performed hyper-parameter search to find best performing model. 
\BulletItem Evaluated models and found results that suggest innate biases may be necessary for a neural network to acquire human language. 



%%%%%%%%%%%%%%%%
%% LEADERSHIP %%
%%%%%%%%%%%%%%%%

\Section
{Leadership}
{Leadership}
{PDF:Leadership}

\Entry
\href{http://outdoors.johnshopkins.edu}
{\textbf{Johns Hopkins Outdoors Club (JHOC)}},
Leader
\hfill
\DatestampYMD{2018}{09}{15} --
Present

\Gap
\BulletItem
Coordinated and led free caving, mountain Biking, and climbing trips for undergrads. 
\BulletItem
Organized publicity events. 
\BulletItem
Maintained and updated JHOC website. 

\Gap
\Gap
\Entry
\href{https://johnshopkins.campuslabs.com/engage/organization/jhubadminton}
{\textbf{Johns Hopkins Badminton Club}},
Team Member
\hfill
\DatestampYMD{2018}{07}{15} --
2019

\Gap
\BulletItem Enabled team to place 4th in the East Coast College 1A division. 
\BulletItem Trained team members. 

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills }
{Skills}
{PDF:Skills}

\BulletItem
Programming: Python, C/C++, Java, Bash: known at an intermediate level

\BulletItem
Development: HTML/CSS, JavaScript, php: website design and implementation 

\BulletItem
Version Control: Git

\BulletItem
Frameworks and Libraries: Numpy, Pandas, PyTorch, jQuery

\BulletItem 
Misc: NLP, MTurk, Wilderness First Responder, CPR certified

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RELEVANT COURSEWORK %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Relevant \&\newline
Coursework}
{Relevant \& Coursework}
{PDF:RelevantCoursework}
%TODO: only include the relevant ones
\BulletItem Linear Algebra, Gateway Computing: JAVA, Discrete Math, Intermediate Programming (C, C++), Probability And Statistics, Data Structures (Java), Computer System Fundamentals, Automata and Computation Theory, Machine Learning 

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}
\BulletItem
Dean's List,
(Fall 2018, Fall 2019, Fall 2020)
\hfill
Fall \DatestampY{2018}, Fall \DatestampY{2019} 

\BulletItem
Summer Pura Award
\hfill
Summer \DatestampY{2020}
\begin{Detail}
    \SubBulletItem Grant for summer research, used for deep learning research in the JHU Computational Psycholinguistics Lab. 
\end{Detail}
\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\end{document}
